### 2022-03-08 paper/localpsf.tex
paper edits. improved interpolation section a lot

If $\Aop$ is symmetric, we take advantage of symmetry to construct a more accurate approximation at negligible additional cost. In this case, 
%impulse responses of $\Aop$ are also impulse responses of $\Aop^T$, which may be interpolated in the variable $y$ instead of $x$ to yield a different approximation of $\Phi(y,x)$. 
we combine information from impulse responses of both $\Aop$ and $\Aop^T$ in the interpolation procedure.
% for approximating $\Phi(y,x)$, to get a more accurate approximation at negligible additional cost.
Intuitively, impulse responses of $\Aop$ can be thought of as ``columns'' of $\Phi$, impulse responses of $\Aop^T$ can be thought of as ``rows'' of $\Phi$, and $\Phi(y,x)$ can be thought of as an unknown entry of $\Phi$. Therefore, when $\Aop$ is symmetric, computing a column of $\Aop$ also gives us a row of $\Aop$ for free, so we approximate $\Phi(y,x)$ using information from a combination of known columns and rows, rather than just known columns.

>>>>

If $\Aop$ is symmetric, we take advantage of symmetry to construct a more accurate approximation at negligible additional cost
%. In this case, 
%impulse responses of $\Aop$ are also impulse responses of $\Aop^T$, which may be interpolated in the variable $y$ instead of $x$ to yield a different approximation of $\Phi(y,x)$. 
%we combine 
by combining information from impulse responses of both $\Aop$ and $\Aop^T$ in the interpolation procedure.
% for approximating $\Phi(y,x)$, to get a more accurate approximation at negligible additional cost.
Intuitively, impulse responses of $\Aop$ can be thought of as ``columns'' of $\Phi$, impulse responses of $\Aop^T$ can be thought of as ``rows'' of $\Phi$, and $\Phi(y,x)$ can be thought of as an unknown entry of $\Phi$. Therefore, when $\Aop$ is symmetric, computing a column of $\Aop$ also gives us a row of $\Aop$ for free, so we approximate $\Phi(y,x)$ using information from a combination of known columns and rows, rather than just known columns.
